%-------------------------
% Resume in Latex
% Author : Ashwin S
% Date   : June 2024
% Based off of: https://github.com/sb2nov/resume
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\usepackage{graphicx}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\RequirePackage{tikz}
\RequirePackage{xcolor}
\RequirePackage{fontawesome}
\usepackage{tikz}
\usetikzlibrary{svg.path}


\definecolor{cvblue}{HTML}{0E5484}
\definecolor{black}{HTML}{130810}
\definecolor{darkcolor}{HTML}{0F4539}
\definecolor{cvgreen}{HTML}{3BD80D}
\definecolor{taggreen}{HTML}{00E278}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{name}{black}
\colorlet{tagline}{darkcolor}
\colorlet{heading}{darkcolor}
\colorlet{headingrule}{cvblue}
\colorlet{accent}{darkcolor}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{\large#1} & \textbf{\small #2} \\
      \textit{\large#3} & \textit{\small #4} \\
      
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}


\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}


\newcommand\sbullet[1][.5]{\mathbin{\vcenter{\hbox{\scalebox{#1}{$\bullet$}}}}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------


\begin{center}
    {\Huge \scshape Ashwin S} \\ \vspace{1pt}
    Thiruvananthapuram, Kerala \\ \vspace{1pt}
    \small \href{tel:+919447726621}{ \raisebox{-0.1\height}\faPhone\ \underline{+91-9447726621} ~} \href{mailto:ashsanthosh8@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{ashsanthosh8@gmail.com}} ~ 
    \href{https://www.linkedin.com/in/ashwin-s-67877728a}{\raisebox{-0.2\height}\faLinkedinSquare\ \underline{LinkedIn}}  ~
    \href{https://github.com/Shanwis}{\raisebox{-0.2\height}\faGithub\ \underline{Github}} ~
    \href{https://leetcode.com/u/SHANWIS/}{\raisebox{-0.2\height}\faCode\ \underline{LeetCode}}
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Indian Institute of Information Technology, Kottayam}{Expected: April 2027}
      {Bachelor of Technology -- Computer Science and Engineering (GPA: 8.75)}{Kottayam, India}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework:} Operating Systems, Computer Networks, Data Structures and Algorithms, Machine Learning, Parallel and Distributed Computing, High Performance Computing}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------WORK EXPERIENCE-----------
\section{WORK EXPERIENCE}
  \resumeSubHeadingListStart

    \resumeSubheading
      {State Forensic Science Laboratory, Kerala}{June 2025 -- July 2025} 
      {\underline{Software Development Intern}}{Thiruvananthapuram, India}
      \resumeItemListStart
        \resumeItem{Developed a secure, production-grade VB.NET desktop application with a SQL Server backend for forensic report management in the Chemistry Division.}
        \resumeItem{Designed normalized relational schemas for cases, items, scopes, categories, and test results, ensuring data integrity and traceability.}
        \resumeItem{Automated standard-compliant forensic report generation using Microsoft Word Interop, producing print-ready .docx documents from .dotx templates.}
      \resumeItemListEnd
      
    \resumeSubheading
      {AleeOop}{Sep. 2024 -- Dec. 2024} 
      {\underline{Quality Assurance Intern}}{Iowa City-Cedar Rapids Area, Remote}
      \resumeItemListStart
        \resumeItem{Performed cross-platform functional and manual testing, and identified, documented, and reported bugs to ensure a seamless user experience across devices.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------RELEVANT PROJECTS-----------
\section{RELEVANT PROJECTS}
    \vspace{-5pt}
    \resumeSubHeadingListStart
    
       \resumeProjectHeading
          {\href{https://github.com/Shanwis/MaQrel}{\textbf{\large{{MaQrel: A Quantum Simulator}}} \raisebox{-0.1\height}\faExternalLink } $|$ \emph{C++, OpenMP, MPI}}{}
          \resumeItemListStart
            \resumeItem{Built a modular C++ quantum simulation library from the ground up, implementing a full state vector model for N-qubit systems.}
            \resumeItem{Engineered high-performance parallel versions using OpenMP for multi-threading and MPI for distributed memory, directly aligning with low-latency scientific computing needs.}
            \resumeItem{Analyzed parallel scalability and identified memory and synchronization bottlenecks across OpenMP and MPI implementations.}
            \resumeItem{Designed as a reusable static library with well-defined headers for modular integration.}
          \resumeItemListEnd 
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\href{https://github.com/Shanwis/Toy-Virtual-Machine}{\textbf{\large{{C Stack Based Virtual Machine}}} \raisebox{-0.1\height}\faExternalLink } $|$ \emph{C, Assembly}}{}
          \resumeItemListStart
            \resumeItem{Architected a Stack Based Virtual Machine and assembler to execute low-level assembly-like programs in C.}
            \resumeItem{Implemented a set of 18 instructions to manage 6 general purpose registers (A-F), the stack pointer (SP), and the instruction pointer (IP).}
          \resumeItemListEnd
          \vspace{-13pt}
          
      \resumeProjectHeading
          {\href{https://github.com/Shanwis/Hey-Teddy}{\textbf{\large{{Hey-Teddy -- Offline Voice Assistant}}} \raisebox{-0.1\height}\faExternalLink } $|$ \emph{Python, VOSK, Porcupine}}{}
          \resumeItemListStart
            \resumeItem{Built an offline voice assistant in Python using VOSK (speech-to-text) and Porcupine (wake-word detection).}
            \resumeItem{Implemented an event-driven offline voice interaction pipeline integrating wake-word detection, speech recognition, and OS-level command execution.}
            \resumeItem{Focused on edge-AI design principles: offline operation, low latency, and minimal compute overhead.}
          \resumeItemListEnd 
          
    \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------VOLUNTEERING & LEADERSHIP-----------
\section{VOLUNTEERING \& LEADERSHIP}
  \resumeSubHeadingListStart

    \resumeSubheading
      {BetaLabs: IoT \& Cloud Computing, IIIT Kottayam}{Ongoing} 
      {{Lead}}{Kottayam, India}
      \resumeItemListStart
        \resumeItem{Coordinated technical workshops and peer learning sessions on IoT and cloud fundamentals.}
      \resumeItemListEnd

    \resumeSubheading
      {Game Dev Utopia, IIIT Kottayam}{Ongoing} 
      {{Lead}}{Kottayam, India}
      \resumeItemListStart
        \resumeItem{Mentored peers in game development projects and assisted in technical planning and execution.}
      \resumeItemListEnd
      
  \resumeSubHeadingListEnd
\vspace{-12pt}

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{\normalsize{Programming:}}{ \normalsize{C++, Python, C, Embedded C++}} \\
     \textbf{\normalsize{Systems \& Performance:}}{ \normalsize{Linux, OpenMP, MPI, Multithreading, POSIX Concepts}} \\
     \textbf{\normalsize{Tools \& Infrastructure:}}{\normalsize{ Git, Docker, SQL Server, MySQL, .NET, ESP32, Arduino Toolchain}} \\
     \textbf{\normalsize{Scientific \& Specialized:}}{\normalsize{ Quantum State-Vector Simulation, Linear Algebra, Numerical Computing}}
    }}
 \end{itemize}
 \vspace{-15pt}

\end{document}